Causal Bandits: Learning Good Interventions via Causal Inference

### 2016-05-19 causal-bandit/nips_2016/discussion.tex
updates

Algorithm~\ref{alg:general} for general causal bandit problems adaptively estimates the reward for all allowable interventions $a \in \calA$ over $T$ rounds by sampling and applying interventions from a distribution $\eta$.
Theorem~\ref{thm:general} shows that this algorithm has (up to log factors) simple regret that is $\bigo{\sqrt{m(\eta)/T}}$ and that the parameter $m(\eta)$ is always less than $N$.
The value of $m(\eta)$ is a uniform bound on the variance of the reward estimators $\hat{\mu}_a$ and, intuitively, problems where all variables' values in the causal model ``occur naturally'' when interventions are sampled from $\eta$ will have low values of $m(\eta)$.

>>>>

Algorithm~\ref{alg:general} for general causal bandit problems 
estimates the reward for all allowable interventions $a \in \calA$ over $T$ rounds by sampling and applying interventions from a distribution $\eta$.
Theorem~\ref{thm:general} shows that this algorithm has (up to log factors) simple regret that is $\smash{\mathcal O(\sqrt{m(\eta)/T)}}$ where 
the parameter $m(\eta)$ measures the difficulty of learning the causal model and is always less than $N$.
The value of $m(\eta)$ is a uniform bound on the variance of the reward estimators $\hat{\mu}_a$ and, intuitively, problems where all variables' values in the causal model ``occur naturally'' when interventions are sampled from $\eta$ will have low values of $m(\eta)$.
